Notes on two photon scattering of the molecular state

### 2019-11-27 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Fixes and corrections

\[ \gamma=\Gamma\frac{\Omega_1\Omega_2}{\Delta^2} \]

@@

The two kinds of ground state scattering measurements we have are atomic state PA rate
and molecular state scattering (using Raman transition).
Assuming the laser is clean and no other states are involved,
\begin{enumerate}
\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
  one frequency so the Raman process can only come back down to the same energy as
  the initial state, which is not in an continuum.
\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
  similarly, the only energy the molecular state could couple to is the initial energy
  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
  The atomic state can indeed be coupled to the continuum but it should be much weaker than
  the molecular state (the up leg is much smaller) and we have not measured a decrease in
  atomic 2-body lifetime when the Raman beam is turned on.
\end{enumerate}
Therefore, in order to generate any loss from this process for the ground state,
we need to have either,
\begin{enumerate}
\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
  can couple the state of interest to the motional continuum. Or,
\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
  can couple to.\\
  Candidate for this continuum includes the center of mass (COM) motional states and
  the motional continuum from other HF states.\\
  The COM motional continuum actually also starts at a positive energy so it doesn't seem
  possible. The continuum from other HF states is much more promising especially since
  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
  the HF state with the lowest energy.
\end{enumerate}

@@

\eqar{
  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
}

>>>>

\[ \gamma=\Gamma\frac{\Omega_1\Omega_2}{4\Delta^2} \]

@@

The two kinds of ground state scattering measurements we have are atomic state PA rate
and molecular state scattering (using Raman transition).
Assuming the laser is clean and no other states are involved,
\begin{enumerate}
\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
  one frequency so the Raman process can only come back down to the same energy as
  the initial state, which is not in an continuum.
\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
  similarly, the only energy the molecular state could couple to is the initial energy
  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
  The atomic state can indeed be coupled to the continuum but it should be much weaker than
  the molecular state (the up leg is much smaller) and we have not measured a decrease in
  atomic 2-body lifetime when the Raman beam is turned on.
\end{enumerate}
Therefore, in order to generate any loss from this process for the ground state,
we need to have either,
\begin{enumerate}
\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
  can couple the state of interest to the motional continuum. Or,
\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
  can couple to.\\
  Candidate for this continuum includes the center of mass (COM) motional states and
  the motional continuum from other HF states.\\
  The COM motional continuum actually also starts at a positive energy so it doesn't seem
  possible. The continuum from other HF states is much more promising especially since
  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
  \sout{However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
    the HF state with the lowest energy.}
  Kang-Kuen and Kenneth pointed out that $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!1, m_{F}^{\mathrm{Na}}\!=\!1\rangle$ is the state with the lowest energy
  so $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ indeed have a (in fact, multiple Zeeman states) continuum to couple to.
\end{enumerate}

@@

\eqar{
  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
}
where $\psi'(r=0)$ is the value of the wavefunction for the other motional state at $r=0$.\\
